---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
gdp_df <- read_csv("C:/Users/ndidi/Documents/NSS_Projects/tidyverse-un-ndidiox/data/gdp_per_capita.csv")

gdp_df
```
```{r}
gdp_df |> head(10)
```
```{r}
gdp_df |> tail(10)
```
```{r}
gdp_df <- select(gdp_df, -"Value Footnotes")
```

```{r}
gdp_df <- rename(gdp_df, "Country" = "Country or Area", "GDP_Per_Capita" = "Value")
```

# 3. Which years are represented in this dataset? How many observations are there per year? Make a plot to view the number of observations per year.
```{r}
gdp_df |> 
  count(Year)
```
# 1999 - 2020 are represented in the dataset.


# 4. How many countries are represented in this dataset? Which countries have the fewest observations?
```{r}
gdp_df |> count(Country)
```

# 5. Create a new dataframe by subsetting `gdp_df` to just the year 2014. Call this new dataframe `gdp_2014`.
```{r}
gdp_2014 <- gdp_df |> 
  filter(Year == 2014)

gdp_2014
```

#6. Use `.describe()` to find the summary statistics for GDP per capita in 2014. 

```{r}
gdp_2014 |> summarize(GDP_Per_Capita)
```

